---
title: "Global ETF Monitoring"
author: "QAE_Student_Dominusmaximus"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = FALSE, message=FALSE, warning=FALSE}
rm(list = ls())
options(scipen = 10)

library(dplyr)
library(openxlsx)
library(tidyquant)
library(tidyverse)
library(stringr)
library(lubridate)
library(htmlwidgets)
library(sparkline)
library(DT)
library(quantmod)

source("ETF_MONIT.R")

end.date <- Sys.Date()

raw.aa.data <- read.xlsx("ETF_LIST.xlsx", sheet = 1) %>% as.tibble()
raw.etf.profile <- readRDS("ETF_PROFILE.rds")
```

***

# Key Markets

***

```{r key_markets, echo = FALSE, message=FALSE, warning=FALSE}
aa.etf.ticker <- raw.aa.data %>% 
  filter(class_1 == "key_market") %>%
  select(symbol) %>% pull

etf.profile <- raw.etf.profile %>% 
  unnest() %>% filter(TICKER %in% aa.etf.ticker)

aa.monit.func(aa.etf.ticker = aa.etf.ticker, 
              etf.profile = etf.profile, 
              end.date = end.date)
```

***

## 1. Equity

***

### 1.1 Regional ETFs

```{r eq_regional, echo = FALSE, message=FALSE, warning=FALSE}
aa.etf.ticker <- raw.aa.data %>% 
  filter(class_1 == "equity_region") %>%
  select(symbol) %>% pull

etf.profile <- raw.etf.profile %>% 
  unnest() %>% filter(TICKER %in% aa.etf.ticker)

aa.monit.func(aa.etf.ticker = aa.etf.ticker, 
              etf.profile = etf.profile,
              end.date = end.date)
```

### 1.1.1 Developed Markets ETFs

```{r eq_developed, echo = FALSE, message=FALSE, warning=FALSE}
aa.etf.ticker <- raw.aa.data %>% 
  filter(class_1 == "equity_country", class_2 == "MSCI Developed Markets") %>%
  select(symbol) %>% pull

etf.profile <- raw.etf.profile %>% 
  unnest() %>% filter(TICKER %in% aa.etf.ticker)

aa.monit.func(aa.etf.ticker = aa.etf.ticker, 
              etf.profile = etf.profile,
              end.date = end.date)
```

### 1.1.2 Emerging Markets ETFs

```{r eq_emerging, echo = FALSE, message=FALSE, warning=FALSE}
aa.etf.ticker <- raw.aa.data %>% 
  filter(class_1 == "equity_country", class_2 != "MSCI Developed Markets") %>%
  select(symbol) %>% pull

etf.profile <- raw.etf.profile %>% 
  unnest() %>% filter(TICKER %in% aa.etf.ticker)

aa.monit.func(aa.etf.ticker = aa.etf.ticker, 
              etf.profile = etf.profile,
              end.date = end.date)
```

### 1.2 U.S. Markets ETFs

#### 1.2.1 U.S. Summary

```{r eq_us_sum, echo = FALSE, message=FALSE, warning=FALSE}
aa.etf.ticker <- c("SPY","DIA","IWM","QQQ")

etf.profile <- raw.etf.profile %>% 
  unnest() %>% filter(TICKER %in% aa.etf.ticker)

aa.monit.func(aa.etf.ticker = aa.etf.ticker, 
              etf.profile = etf.profile,
              end.date = end.date)
```

#### 1.2.2 S&P Indexes

```{r eq_sp, echo = FALSE, message=FALSE, warning=FALSE}
aa.etf.ticker <- raw.aa.data %>% 
  filter(class_1 == "equity_us", class_2 == "SP") %>%
  select(symbol) %>% pull

etf.profile <- raw.etf.profile %>% 
  unnest() %>% filter(TICKER %in% aa.etf.ticker)

aa.monit.func(aa.etf.ticker = aa.etf.ticker, 
              etf.profile = etf.profile,
              end.date = end.date)
```

#### 1.2.3 Russell Indexes
```{r eq_russell, echo = FALSE, message=FALSE, warning=FALSE}
aa.etf.ticker <- raw.aa.data %>% 
  filter(class_1 == "equity_us", class_2 == "RUSSELL") %>%
  select(symbol) %>% pull

etf.profile <- raw.etf.profile %>% 
  unnest() %>% filter(TICKER %in% aa.etf.ticker)

aa.monit.func(aa.etf.ticker = aa.etf.ticker, 
              etf.profile = etf.profile,
              end.date = end.date)
```

#### 1.2.4 NASDAQ Indexes
```{r eq_nasdaq, echo = FALSE, message=FALSE, warning=FALSE}
aa.etf.ticker <- raw.aa.data %>% 
  filter(class_1 == "equity_us", class_2 == "NASDAQ") %>%
  select(symbol) %>% pull

etf.profile <- raw.etf.profile %>% 
  unnest() %>% filter(TICKER %in% aa.etf.ticker)

aa.monit.func(aa.etf.ticker = aa.etf.ticker, 
              etf.profile = etf.profile,
              end.date = end.date)
```

### 1.3 Sector ETFs

#### 1.3.1 Global Sector ETFs
```{r eq_sector_global, echo = FALSE, message=FALSE, warning=FALSE}
aa.etf.ticker <- raw.aa.data %>% 
  filter(class_1 == "equity_sector", class_2 == "global") %>%
  select(symbol) %>% pull

etf.profile <- raw.etf.profile %>% 
  unnest() %>% filter(TICKER %in% aa.etf.ticker)

aa.monit.func(aa.etf.ticker = aa.etf.ticker, 
              etf.profile = etf.profile,
              end.date = end.date)
```

#### 1.3.2 U.S. Sector ETFs
```{r eq_sector_us, echo = FALSE, message=FALSE, warning=FALSE}
aa.etf.ticker <- raw.aa.data %>% 
  filter(class_1 == "equity_sector", class_2 == "SPDR") %>%
  select(symbol) %>% pull

etf.profile <- raw.etf.profile %>% 
  unnest() %>% filter(TICKER %in% aa.etf.ticker)

aa.monit.func(aa.etf.ticker = aa.etf.ticker, 
              etf.profile = etf.profile,
              end.date = end.date)
```

#### 1.3.3 Themes & SubSectors ETFs

#### 1.3.3.1 Energy & Alternative Energy

```{r eq_sector_sub_Energy, echo = FALSE, message=FALSE, warning=FALSE}
aa.etf.ticker <- raw.aa.data %>% 
  filter(class_1 == "equity_subsector", 
         class_2 %in% c("Energy","Alternative Energy")) %>%
  select(symbol) %>% pull

etf.profile <- raw.etf.profile %>% 
  unnest() %>% filter(TICKER %in% aa.etf.ticker)

aa.monit.func(aa.etf.ticker = aa.etf.ticker, 
              etf.profile = etf.profile,
              end.date = end.date)
```

#### 1.3.3.2 Material, Metals and Mining

```{r eq_sector_sub_Material, echo = FALSE, message=FALSE, warning=FALSE}
aa.etf.ticker <- raw.aa.data %>% 
  filter(class_1 == "equity_subsector", 
         class_2 == "Material, Metals and Mining") %>%
  select(symbol) %>% pull

etf.profile <- raw.etf.profile %>% 
  unnest() %>% filter(TICKER %in% aa.etf.ticker)

aa.monit.func(aa.etf.ticker = aa.etf.ticker, 
              etf.profile = etf.profile,
              end.date = end.date)
```

#### 1.3.3.3 Industrial & Infrastructure

```{r eq_sector_sub_Industrial, echo = FALSE, message=FALSE, warning=FALSE}
aa.etf.ticker <- raw.aa.data %>% 
  filter(class_1 == "equity_subsector", 
         class_2 == "Industrial & Infrastructure") %>%
  select(symbol) %>% pull

etf.profile <- raw.etf.profile %>% 
  unnest() %>% filter(TICKER %in% aa.etf.ticker)

aa.monit.func(aa.etf.ticker = aa.etf.ticker, 
              etf.profile = etf.profile,
              end.date = end.date)
```

#### 1.3.3.4 Consumer

```{r eq_sector_sub_Consumer, echo = FALSE, message=FALSE, warning=FALSE}
aa.etf.ticker <- raw.aa.data %>% 
  filter(class_1 == "equity_subsector", 
         class_2 == "Consumer") %>%
  select(symbol) %>% pull

etf.profile <- raw.etf.profile %>% 
  unnest() %>% filter(TICKER %in% aa.etf.ticker)

aa.monit.func(aa.etf.ticker = aa.etf.ticker, 
              etf.profile = etf.profile,
              end.date = end.date)
```

#### 1.3.3.5 Healthcare

```{r eq_sector_sub_Healthcare, echo = FALSE, message=FALSE, warning=FALSE}
aa.etf.ticker <- raw.aa.data %>% 
  filter(class_1 == "equity_subsector", 
         class_2 == "Healthcare") %>%
  select(symbol) %>% pull

etf.profile <- raw.etf.profile %>% 
  unnest() %>% filter(TICKER %in% aa.etf.ticker)

aa.monit.func(aa.etf.ticker = aa.etf.ticker, 
              etf.profile = etf.profile,
              end.date = end.date)
```

#### 1.3.3.6 Financial

```{r eq_sector_sub_Financial, echo = FALSE, message=FALSE, warning=FALSE}
aa.etf.ticker <- raw.aa.data %>% 
  filter(class_1 == "equity_subsector", 
         class_2 == "Financial") %>%
  select(symbol) %>% pull

etf.profile <- raw.etf.profile %>% 
  unnest() %>% filter(TICKER %in% aa.etf.ticker)

aa.monit.func(aa.etf.ticker = aa.etf.ticker, 
              etf.profile = etf.profile,
              end.date = end.date)
```

#### 1.3.3.7 Technology

```{r eq_sector_sub_Technology, echo = FALSE, message=FALSE, warning=FALSE}
aa.etf.ticker <- raw.aa.data %>% 
  filter(class_1 == "equity_subsector", 
         class_2 == "Technology") %>%
  select(symbol) %>% pull

etf.profile <- raw.etf.profile %>% 
  unnest() %>% filter(TICKER %in% aa.etf.ticker)

aa.monit.func(aa.etf.ticker = aa.etf.ticker, 
              etf.profile = etf.profile,
              end.date = end.date)
```

***

## 2. Bond

***

```{r bond, echo = FALSE, message=FALSE, warning=FALSE}
aa.etf.ticker <- raw.aa.data %>% 
  filter(class_1 == "bond") %>%
  select(symbol) %>% pull

etf.profile <- raw.etf.profile %>% 
  unnest() %>% filter(TICKER %in% aa.etf.ticker)

aa.monit.func(aa.etf.ticker = aa.etf.ticker, 
              etf.profile = etf.profile, 
              end.date = end.date,
              bond.opt = T)
```

***

## 3. Commodity

***

#### 3.1 Precious Metals

```{r commodity, echo = FALSE, message=FALSE, warning=FALSE}
aa.etf.ticker <- raw.aa.data %>% 
  filter(class_1 == "comm2", class_2 == "Precious Metals") %>%
  select(symbol) %>% pull

etf.profile <- raw.etf.profile %>% 
  unnest() %>% filter(TICKER %in% aa.etf.ticker)

aa.monit.func(aa.etf.ticker = aa.etf.ticker, 
              etf.profile = etf.profile, 
              end.date = end.date,
              commo.opt = T)
```

#### 3.2 Energy

```{r commodity_energy, echo = FALSE, message=FALSE, warning=FALSE}
aa.etf.ticker <- raw.aa.data %>% 
  filter(class_1 == "comm2", class_2 == "Energy") %>%
  select(symbol) %>% pull

etf.profile <- raw.etf.profile %>% 
  unnest() %>% filter(TICKER %in% aa.etf.ticker)

aa.monit.func(aa.etf.ticker = aa.etf.ticker, 
              etf.profile = etf.profile, 
              end.date = end.date,
              commo.opt = T)
```

#### 3.3 Agricultural Commodities

```{r commodity_ac, echo = FALSE, message=FALSE, warning=FALSE}
aa.etf.ticker <- raw.aa.data %>% 
  filter(class_1 == "comm2", class_2 == "Agricultural Commodities") %>%
  select(symbol) %>% pull

etf.profile <- raw.etf.profile %>% 
  unnest() %>% filter(TICKER %in% aa.etf.ticker)

aa.monit.func(aa.etf.ticker = aa.etf.ticker, 
              etf.profile = etf.profile, 
              end.date = end.date,
              commo.opt = T)
```

#### 3.4 Industrial Commodities

```{r commodity_ind_comm, echo = FALSE, message=FALSE, warning=FALSE}
aa.etf.ticker <- raw.aa.data %>% 
  filter(class_1 == "comm2", class_2 == "Industrial Commodities") %>%
  select(symbol) %>% pull

etf.profile <- raw.etf.profile %>% 
  unnest() %>% filter(TICKER %in% aa.etf.ticker)

aa.monit.func(aa.etf.ticker = aa.etf.ticker, 
              etf.profile = etf.profile, 
              end.date = end.date,
              commo.opt = T)
```

#### 3.5 Commodity Basket

```{r commodity_basket, echo = FALSE, message=FALSE, warning=FALSE}
aa.etf.ticker <- raw.aa.data %>% 
  filter(class_1 == "comm2", class_2 == "Commodity Basket") %>%
  select(symbol) %>% pull

etf.profile <- raw.etf.profile %>% 
  unnest() %>% filter(TICKER %in% aa.etf.ticker)

aa.monit.func(aa.etf.ticker = aa.etf.ticker, 
              etf.profile = etf.profile, 
              end.date = end.date,
              commo.opt = T)
```

